Report on the Second Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE2)

### 2015-04-25 WSSSPE2_report/WSSSPE2_review.tex
Section 4: rewrite some parts.

\item \textbf{John Peterson: Continuous Integration for Concurrent MOOSE Framework and
Application Development on GitHub.} 
%Affiliation: Idaho National Laboratory
Peterson from the the Idaho National Laboratory reported that in March 2014, the
MOOSE framework was released under an open source license on GitHub,
significantly expanding and diversifying the pool of current active and
potential future contributors on the project. The MOOSE team employs an
extensive continuous integration test suite to ensure that both the framework
and the applications based on the framework are verified before any code changes
are accepted into the repository. They use a combination of built-in git
features such as branching and submodules, GitHub API integration capabilities,
and in-house developed testing software to perform this verification and update
the dependent applications in a relatively seamless manner for users.

\item \textbf{Abani Patra: Execute it.}
%Univ at Buffalo, SUNY
Patra discussed the value of
an available and easily accessible platform for executing scientific software,
e.g., HUBzero, to access XSEDE or other computing resources.
Such a platform for executing benchmark problems (even at small
scale) allows the developer community access to a reference implementation and
provides an easy way to train the larger user community. A second focus of this
presentation was the idea that much more attention needs to be paid to the
integrated use of simulation tools inside complex workflows. True usability
needs supporting the user community workflow. \todo{revise}

@@

\item \textbf{Daniel S. Katz: Implementing Transitive Credit with JSON-LD.}
Science and engineering research increasingly relies on activities that
facilitate research but are not rewarded or recognized, such as: data
sharing; developing common data resources, software and methodologies; and
annotating data and publications. To promote and advance these activities, we
must develop mechanisms for assigning credit, facilitate the appropriate
attribution of research outcomes, devise incentives for activities that
facilitate research, and allocate funds to maximize return on investment. Katz
discussed the issue of assigning credit for both direct and indirect
contributions by using JSON-LD to implement a prototype transitive credit
system~\cite{Katz_transitive_credit_poster}.

>>>>

\item \textbf{John Peterson: Continuous Integration for Concurrent MOOSE Framework and
Application Development on GitHub.} 
%Affiliation: Idaho National Laboratory
Peterson from the Idaho National Laboratory reported that in March 2014, the
MOOSE framework was released under an open source license on GitHub,
significantly expanding and diversifying the pool of current active and
potential future contributors on the project. The MOOSE team employs an
extensive continuous integration test suite to ensure that both the framework
and the applications based on the framework are verified before any code changes
are accepted into the repository. They use a combination of built-in Git
features such as branching and submodules, GitHub API integration capabilities,
and in-house developed testing software to perform this verification and update
the dependent applications in a relatively seamless manner for users.

\item \textbf{Abani Patra: Execute it.}
%Univ at Buffalo, SUNY
Patra discussed the value of
an available and easily accessible platform for executing scientific software,
e.g., HUBzero, to access XSEDE or other computing resources.
Such a platform for executing benchmark problems (even at small
scale) allows the developer community access to a reference implementation and
provides an easy way to train the larger user community. A second idea of this
presentation was that for true usability, much more attention and support needs to be given to the
integrated use of simulation tools inside complex workflows.
%needs supporting the user community workflow.

@@

\item \textbf{Daniel Katz: Implementing Transitive Credit with JSON-LD.}
Science and engineering research increasingly relies on activities that
facilitate research but are not rewarded or recognized, such as: data
sharing; developing common data resources, software and methodologies; and
annotating data and publications. To promote and advance these activities, we
must develop mechanisms for assigning credit, facilitate the appropriate
attribution of research outcomes, devise incentives for activities that
facilitate research, and allocate funds to maximize return on investment. Katz
discussed the issue of assigning credit for both direct and indirect
contributions by using JSON-LD to implement a prototype transitive credit
system~\cite{Katz_transitive_credit_poster}.
